### 2016-02-22 HSF-TN/draft-2016-VACPLAT/draft-HSF-TN-2016-VACPLAT.tex
Clarify use of /proc values etc

The factory messages factory\_query and factory\_status are intended
for monitoring the state of the factories themselves, including
generic Unix health metrics such as free disk and CPU load. As well
as manual queries by administrators, these messages may also be
used for automated Nagios-style monitoring and alarms.

@@

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``factory\_status''
\item[vac\_version] Software version of Vac
\item[vacquery\_version] Version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[time\_sent] Time in Unix seconds
\item[total\_cpus] Number of (logical) processors available to VMs
\item[running\_cpus] Number of processors assigned to running VMs
\item[running\_machines] Number of running VMs
\item[total\_machines] Maximum possible number of VMs
\item[total\_hs06] Total HS06 available to VMs
\item[vac\_disk\_avail\_kb] Free space available in Vac's workspace, in units of 1024 bytes
\item[root\_disk\_avail\_kb] Free space available on the root partition, in units of 1024 bytes
\item[vac\_disk\_avail\_inodes] Free inodes available in Vac's workspace
\item[root\_disk\_avail\_inodes] Free inodes available on the root partition
\item[load\_average] The 15 minute Unix load average on the factory
\item[kernel\_version] The running kernel version of the factory
\item[os\_issue] A string identifying the operating system (typically the first line of /etc/issue)
\item[boot\_time] The time when the factory booted up in Unix seconds
\item[factory\_heartbeat\_time] Time of the last heartbeat created by the VM factory agent in Unix secconds
\item[responder\_heartbeat\_time] Time of the last heartbeat created by the VacQuery responder service in Unix secconds
\item[mjf\_heartbeat\_time] Time of the last heartbeat created by the HTTP Machine/Job Features service in Unix secconds
\item[metadata\_heartbeat\_time] Time of the last heartbeat created by the HTTP Metadata service in Unix secconds
\item[swap\_used\_kb] Swap space in use on the factory, in units of 1024 bytes
\item[swap\_free\_kb] Free swap space, in units of 1024 bytes
\item[mem\_used\_kb] Physical memory in use on the factory, in units of 1024 bytes
\item[mem\_total\_kb] Free physical memory, in units of 1024 bytes
\item[site] Name of the site registered in the GOCDB, or the Vac space name if the site is not registered
\end{description}
\end{quote}

>>>>

The factory messages factory\_query and factory\_status are intended
for monitoring the state of the factories themselves, including
generic Linux health metrics such as free disk and CPU load. As well
as manual queries by administrators, these messages may also be
used for automated Nagios-style monitoring and alarms.

@@

The format and units of the disk and memory values are
aligned with the values returned by the relevant system
calls and the /proc interface.

\begin{quote}
\begin{description}
\setlength{\parskip}{0pt}
\item[message\_type] ``factory\_status''
\item[vac\_version] Software version of Vac
\item[vacquery\_version] Version of the VacQuery protocol
\item[cookie] Matching the value supplied by the recipient
\item[space] Vac space name
\item[factory] FQDN of the factory
\item[time\_sent] Time in Unix seconds
\item[site] Name of the site registered in the GOCDB, or the Vac space name if the site is not registered
\item[total\_cpus] Number of (logical) processors available to VMs
\item[running\_cpus] Number of processors assigned to running VMs
\item[running\_machines] Number of running VMs
\item[total\_machines] Maximum possible number of VMs
\item[total\_hs06] Total HS06 available to VMs
\item[boot\_time] The time when the factory booted up in Unix seconds
\item[factory\_heartbeat\_time] Time of the last heartbeat created by the VM factory agent in Unix secconds
\item[responder\_heartbeat\_time] Time of the last heartbeat created by the VacQuery responder service in Unix secconds
\item[mjf\_heartbeat\_time] Time of the last heartbeat created by the HTTP Machine/Job Features service in Unix secconds
\item[metadata\_heartbeat\_time] Time of the last heartbeat created by the HTTP Metadata service in Unix secconds
\item[vac\_disk\_avail\_kb] Free space available in Vac's workspace, in units of 1024 bytes
\item[root\_disk\_avail\_kb] Free space available on the root partition, in units of 1024 bytes
\item[vac\_disk\_avail\_inodes] Free inodes available in Vac's workspace
\item[root\_disk\_avail\_inodes] Free inodes available on the root partition
\item[load\_average] The 15 minute load average on the factory
\item[kernel\_version] The kernel version of the factory
\item[os\_issue] A string identifying the operating system (typically the first line of /etc/issue)
\item[swap\_used\_kb] Swap space in use on the factory, in units of 1024 bytes
\item[swap\_free\_kb] Free swap space, in units of 1024 bytes
\item[mem\_used\_kb] Physical memory in use on the factory, in units of 1024 bytes
\item[mem\_total\_kb] Free physical memory, in units of 1024 bytes
\end{description}
\end{quote}
